\section{Download (Cloning)}
\label{nedlasting}
If you already have the project stored locally on you're machine, you can safely skip to (\ref{oppdatere}).
\subsection{Mac OS or Linux}
\begin{enumerate}
    \item Open a \textit{Terminal} window.
    \item Configuration of \textit{Git} (Skip if already configured):
        \begin{enumerate}
            \item Setting your username in \textit{Git} [\ref{username}]:
            \shellcmd{git config --global user.name "Mona Lisa"}
            \\The username is used by \textit{Git} to identify your commits. It doesn't have to be the same as on your \textit{Github}-account.
            \item Setting your commit email address in \textit{Git} [\ref{email}]:
            \shellcmd{git config --global user.email "email@example.com"}
            \\The email address should be the same as the one associated with your \textit{Github}-account.
        \end{enumerate}
    \item Enter the command:
    \\
    $$\shellcmd{git clone https://github.com/LasseNatvig/SimComp.git <PATH/NEWFOLDER>}$$
    \\
    PATH should be replaced with the path to where you want to store the project. NEWFOLDER should be replaced by the folder name in which to store the project.
    \item If the download was successful you should be able to change to that directory and list the content. Test by entering the following commands:\\
    $$\shellcmd{cd <PATH/NEWFOLDER>}$$
    $$\shellcmd{ls}$$\\
    The content should look something like this:\\
    $$\texttt{LICENSE  README.md   \_Console   \_GUI   \_Simulator   \_Wiki}$$\\
    
\end{enumerate}

\subsection{Windows}
\begin{enumerate}
    \item Open \textit{Visual Studio 2017}.
    \item Click on the \textit{View} button in the menu bar, then choose \textit{Team Explorer}.
    \item In the \textit{Team Explorer} window click \textit{Clone} under  \textit{Local Git Repositories}.
    \item In the top field, paste: \url{https://github.com/LasseNatvig/SimComp.git}. Then click on
    % TODO, sjekk .. grønn stikkkontakt?, er Clone grønn --- sjekk detaljer for MS-VS-Community 2019
    \textit{Clone}. The project will be saved in the folder given by the input field underneath.
\end{enumerate}
If the cloning was successful, you should have a folder named \textit{SimComp} under \textit{Local Git Repositories}.
% TODO krever vel at en angir det navnet SimComp