\section{Update (Sync/Pull)} \label{oppdatere}

The version control system \textit{Git} uses branches, each branch contains a version of the project. The branch named \textit{Master} is often supposed to be a working version without bugs, it is most likely the branch you want to update. 
% TODO Lasse mulig noe manglet her pga. cmake, fikk ikke frem filene i solution explorer?
\subsection{Mac OS or Linux}
\begin{enumerate}
    \item Open a \textit{Terminal} window
    \item Change to the project directory:
    \shellcmd{cd <PROJECTPATH>}
    \item Update branches:
    \shellcmd{git fetch}
    \item  Make sure that you're on the right branch (Skip if you already know):
    \begin{enumerate}
        \item List branches:
        \shellcmd{git branch} \\
        The * symbol indicates the branch that you're on.  
        \item Change branch if necessary:
        \shellcmd{git checkout <BRANCH>}
    \end{enumerate}
    \item Update branch from remote (\textit{Github}):
    \shellcmd{git pull}
    \item Make sure that everything is up-to-date:
    \shellcmd{git status}\\
    This should display the message: \\
    "\texttt{On branch <BRANCH>\\
    Your branch is up-to-date with 'origin/<BRANCH>'.\\
    nothing to commit, working tree clean}"
    
\end{enumerate}

\subsection{Windows}
\begin{enumerate}
    \item Open \textit{Visual Studio 2017}.
    % TODO change to (1) MS VS community 2019 (2) later try also VS code
    \item Navigate to \textit{File} \(\rightarrow\) \textit{Folder} \(\rightarrow\) \textit{Open} in the menu bar.
    \item Choose the \textit{SimComp} folder.
    \item Navigate to \textit{View} \(\rightarrow\) \textit{Team Explorer} in the menu bar.
    \item In the \textit{Team Explorer}-window, click on \textit{SimComp} under \textit{Local Git Repositories}.
    \item Make sure that you're on the right branch (Skip if you already know):
        \begin{enumerate}
            \item Click on \textit{Branches} under \textit{project}.
            \item Under \textit{Active Git Repositories}, make sure that the name of the branch you wish to update is the one enclosed in parenthesis next to "SimComp".
            \item If you wish to change branch you'll have to double click that branch. \textbf{Note} that branches that does not exist locally is found under \textit{remotes/origin}.
            \item Navigate one page back by clicking the back button in the top left corner. 
        \end{enumerate}
    \item Click on \textit{Sync} under \textit{project}.
    \item Sync by clicking \textit{Sync}.
    % Note: Lasse needed github extensions to do this
    \item A successful update(sync) is indicated by the message: \textit{Successfully synchronized incoming and outgoing commits.}
    % TODO check ... my version ssays: there are no incoming ... no outgoing ... , wait till we are using MSVS community 2019
\end{enumerate}

By now the project should be up to date and ready to be built.\\
\textbf{Note} that if you're on a different branch than \textit{Master}, the code might not compile.